Raft Distributed Consensus Algorithm over\\ WebRTC (Web Real-Time Communication)

### 2015-10-06 research_class/paper.tex
paper.tex: remove obsolete text.
process.py: split output / average. Update 1000ms data.

%%\usepackage{geometry}
%%\geometry{margin=2.0cm}
%%
%%\usepackage[backend=bibtex]{biblatex}
%%
\usepackage{hyperref}
%%\usepackage{caption}
%%\usepackage{subcaption}
%%
%%\usepackage{authblk}
%%
%%\usepackage{microtype}

@@

%%\title{Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)}
%%
%%\author{Joel D. Martin}
%%\author{David Levine}
%%\affil{University of Texas at Arlington}
%%
%%\addbibresource{references/raft.bib}
%%\addbibresource{references/w3c.bib}
%%\addbibresource{references/ietf.bib}
%%\addbibresource{references/other.bib}

@@

% TODO: programmatic figure numbers
Figure 7 shows the results of running the
\emph{test/test\_chat\_propagate.js} test to show the amount of time
that a stable cluster takes to propagate, commit and apply a single
state machine command to the state machines on every cluster node.

Figure 7 is a scatterplot with each test run as a blue ``x" and a black
line representing the average at each cluster size.

\begin{figure}[!t]
    \begin{tikzpicture}
    \begin{axis}[%
        xlabel={Nodes}, ylabel={Time (seconds)},
        xtick=data,
        grid=major,
        scatter/classes={%
            propagate={mark=x,draw=blue},
            propagate_average={mark=,draw=red}}]
    \addplot[scatter,only marks,%
        scatter src=explicit symbolic]%
    table[meta=label] {data/data_propagate.dat};
    \addplot[scatter,%
        scatter src=explicit symbolic]%
    table[meta=label] {data/data_propagate_averages.dat};
    \end{axis}
    \end{tikzpicture}
\caption{Propagate$,$ Commit$,$ and Apply Command}
  \label{fig:propagate}
\end{figure}

Figures 8, 9 and 10 show the results of running the
\emph{test/test\_up.js} and \emph{test/test\_kill\_nodes.js} in both
modes (kill only leader and kill just under half the nodes). Three
different scatterplots are shown for each test mode to test different
values of the Raft election timeout value: 100ms, 500ms, and 1000ms.
The election timeout value makes very little difference to the average
time curve line. The reason for this is that the first leader tends to
stay the leader as new nodes are added so for the most part the
election timer does not have an impact.

@@

\begin{enumerate}
    \item \emph{Figure 8 (a)}: The results show that once the cluster
        size reaches 17, the cluster sometimes does not activate
        before the test times out (the red ``x" marks). Once the
        cluster reaches 21 nodes, all 7 test runs time out. The reason
        for this is because at 17 nodes, the leader is not always able
        to send out appendEntries RPCs to all the other nodes before
        their election timeout fires. More analysis is needed, but one
        possible explanation is that the single SlimerJS XULRunner
        process that is handling all the cluster nodes is not able to
        give enough CPU time to the leader node to reliably send
        appendEntries RPCs to all the other nodes within the election
        timeout value. Increasing the election timeout to 500ms or
        greater eliminates the failures without significantly changing
        the average cluster activation time curve.
    \item \emph{Figure 9 (a)}: The results show that when the cluster
        size reaches 15, then average amount of time for cluster
        recovery (after the leader is killed) increases dramatically
        (not all data points are shown on the plot for size 15). At
        cluster size 17 the cluster is no longer able to recover
        within the test timeout period. Increasing the election
        timeout to 500ms or greater eliminates the failures at the
        cost of slightly increased recovery time for smaller cluster
        sizes.
    \item \emph{Figure 10 (a)}: During this test the cluster was unable to
        activate at cluster size 21 when the election timeout value is
        set to 100ms (see Figure 8 (a)). This means there was no
        opportunity for cluster recovery at cluster size 21 so there
        is no data for that column.

@@

%\begin{figure*}[!t]
\begin{figure*}[h]
    \centering
    %\begin{subfigure}[b]{0.30\textwidth}
    \subfloat[100ms election timer]{
        \centering
        \resizebox{0.3\linewidth}{!}{
            \begin{tikzpicture}
            \begin{axis}[%
                %height=1.5\textwidth, width=1.4\textwidth,
                xlabel={Nodes}, ylabel={Time (seconds)},
                xtick=data,
                ymin=0, ymax=65,
                grid=major,
                scatter/classes={%
                    et100={mark=x,draw=blue},
                    et100_fail={mark=x,draw=red},
                    et100_average={mark=,draw=red}}]
            \addplot[scatter,only marks,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_cluster_up_100.dat};
            \addplot[scatter,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_cluster_up_100_averages.dat};
            \end{axis}
            \end{tikzpicture}
        }
        \label{fig:A}
    }
    %\begin{subfigure}[b]{0.30\textwidth}
    \subfloat[500ms election timer]{
        \centering
        \resizebox{0.3\linewidth}{!}{
            \begin{tikzpicture}
            \begin{axis}[%
                %height=1.5\textwidth, width=1.4\textwidth,
                xlabel={Nodes}, ylabel={Time (seconds)},
                xtick=data,
                ymin=0, ymax=65,
                grid=major,
                scatter/classes={%
                    et500={mark=x,draw=blue},
                    et500_average={mark=,draw=red}}]
            \addplot[scatter,only marks,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_cluster_up_500.dat};
            \addplot[scatter,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_cluster_up_500_averages.dat};
            \end{axis}
            \end{tikzpicture}
        }
        \label{fig:B}
    }
    %\begin{subfigure}[b]{0.30\textwidth}
    \subfloat[1000ms election timer]{
        \centering
        \resizebox{0.3\linewidth}{!}{
            \begin{tikzpicture}
            \begin{axis}[%
                %height=1.5\textwidth, width=1.4\textwidth,
                xlabel={Nodes}, ylabel={Time (seconds)},
                xtick=data,
                ymin=0, ymax=65,
                grid=major,
                scatter/classes={%
                    et1000={mark=x,draw=blue},
                    et1000_average={mark=,draw=red}}]
            \addplot[scatter,only marks,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_cluster_up_1000.dat};
            \addplot[scatter,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_cluster_up_1000_averages.dat};
            \end{axis}
            \end{tikzpicture}
        }
        \label{fig:C}
    }
    \caption{Initial Cluster Activation}
    \label{fig:cluster_up}

@@

    %\begin{subfigure}[b]{0.30\textwidth}
    \subfloat[100ms election timer]{
        \centering
        \resizebox{0.3\linewidth}{!}{
            \begin{tikzpicture}
            \begin{axis}[%
                %height=1.5\textwidth, width=1.4\textwidth,
                xlabel={Nodes}, ylabel={Time (seconds)},
                xtick=data,
                ymin=0, ymax=3.5, xmax=23,
                grid=major,
                scatter/classes={%
                    kl={mark=x,draw=blue},
                    kl_fail={mark=x,draw=red},
                    kl_average={mark=,draw=red}}]
            \addplot[scatter,only marks,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_kill_leader_100.dat};
            \addplot[scatter,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_kill_leader_100_averages.dat};
            \end{axis}
            \end{tikzpicture}
        }
        \label{fig:D}
    }
    %\begin{subfigure}[b]{0.30\textwidth}
    \subfloat[500ms election timer]{
        \centering
        \resizebox{0.3\linewidth}{!}{
            \begin{tikzpicture}
            \begin{axis}[%
                %height=1.5\textwidth, width=1.4\textwidth,
                xlabel={Nodes}, ylabel={Time (seconds)},
                xtick=data,
                ymin=0, ymax=3.5,
                grid=major,
                scatter/classes={%
                    kl={mark=x,draw=blue},
                    kl_average={mark=,draw=red}}]
            \addplot[scatter,only marks,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_kill_leader_500.dat};
            \addplot[scatter,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_kill_leader_500_averages.dat};
            \end{axis}
            \end{tikzpicture}
        }
        \label{fig:E}
    }
    %\begin{subfigure}[b]{0.30\textwidth}
    \subfloat[1000ms election timer]{
        \centering
        \resizebox{0.3\linewidth}{!}{
            \begin{tikzpicture}
            \begin{axis}[%
                %height=1.5\textwidth, width=1.4\textwidth,
                xlabel={Nodes}, ylabel={Time (seconds)},
                xtick=data,
                ymin=0, ymax=3.5,
                grid=major,
                scatter/classes={%
                    kl={mark=x,draw=blue},
                    kl_average={mark=,draw=red}}]
            \addplot[scatter,only marks,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_kill_leader_1000.dat};
            \addplot[scatter,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_kill_leader_1000_averages.dat};
            \end{axis}
            \end{tikzpicture}
        }
        \label{fig:F}
    }
    \caption{Recovery from Leader Failure}
    \label{fig:recovery-leader-failure}

@@

    %\begin{subfigure}[b]{0.30\textwidth}
    \subfloat[100ms election timer]{
        \centering
        \resizebox{0.3\linewidth}{!}{
            \begin{tikzpicture}
            \begin{axis}[%
                %height=1.5\textwidth, width=1.4\textwidth,
                xlabel={Nodes}, ylabel={Time (seconds)},
                xtick=data,
                ymin=0, ymax=3.5, xmax=23,
                grid=major,
                scatter/classes={%
                    kh={mark=x,draw=blue},
                    kh_average={mark=,draw=red}}]
            \addplot[scatter,only marks,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_kill_half_100.dat};
            \addplot[scatter,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_kill_half_100_averages.dat};
            \end{axis}
            \end{tikzpicture}
        }
        \label{fig:G}
    }
    %\begin{subfigure}[b]{0.30\textwidth}
    \subfloat[500ms election timer]{
        \centering
        \resizebox{0.3\linewidth}{!}{
            \begin{tikzpicture}
            \begin{axis}[%
                %height=1.5\textwidth, width=1.4\textwidth,
                xlabel={Nodes}, ylabel={Time (seconds)},
                xtick=data,
                ymin=0, ymax=3.5,
                grid=major,
                scatter/classes={%
                    kh={mark=x,draw=blue},
                    kh_average={mark=,draw=red}}]
            \addplot[scatter,only marks,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_kill_half_500.dat};
            \addplot[scatter,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_kill_half_500_averages.dat};
            \end{axis}
            \end{tikzpicture}
        }
        \label{fig:H}
    }
    %\begin{subfigure}[b]{0.30\textwidth}
    \subfloat[1000ms election timer]{
        \centering
        \resizebox{0.3\linewidth}{!}{
            \begin{tikzpicture}
            \begin{axis}[%
                %height=1.5\textwidth, width=1.4\textwidth,
                xlabel={Nodes}, ylabel={Time (seconds)},
                xtick=data,
                ymin=0, ymax=3.5,
                grid=major,
                scatter/classes={%
                    kh={mark=x,draw=blue},
                    kh_average={mark=,draw=red}}]
            \addplot[scatter,only marks,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_kill_half_1000.dat};
            \addplot[scatter,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_kill_half_1000_averages.dat};
            \end{axis}
            \end{tikzpicture}
        }
        \label{fig:I}
    }
    \caption{Recovery from Half Cluster Failure}
    \label{fig:recovery-half-failure}
\end{figure*}

>>>>

\usepackage{hyperref}

@@

@@

Figure~\ref{fig:propagate1} shows the results of running the
\emph{test/wait\_chat\_propagate.js} test to show the amount of time
that a stable cluster takes to propagate, commit and apply a single
chat message to the state machine on every cluster node using the
atomic \emph{seqAppend} command.  Figure~\ref{fig:propagate1} is
a scatterplot with each test run as a blue ``x" and a black line
representing the average at each cluster size.

\begin{figure}[!t]
    \begin{tikzpicture}
    \begin{axis}[%
        xlabel={Nodes}, ylabel={Time (seconds)},
        %xtick=data,
        xmin=0, ymin=0,
        grid=major,
        scatter/classes={%
            propagate_1_et1000={mark=x,draw=blue},
            propagate_1_et1000_average={mark=}}]
    \addplot[scatter,only marks,%
        scatter src=explicit symbolic]%
    table[meta=label] {data/propagate_1.dat};
    \addplot[scatter,%
        scatter src=explicit symbolic]%
    table[meta=label] {data/propagate_1_average.dat};
    \end{axis}
    \end{tikzpicture}
\caption{Propagate$,$ Commit$,$ and Apply Command}
  \label{fig:propagate1}
\end{figure}

Figure~\ref{fig:propagate100} is similar to
Figure~\ref{fig:propagate1} but shows the results of adding 100 chat
messages instead of just 1. The commands are serialized which means
that the previous command must be committed before the current command
can be committed. The test is complete once the last chat message
command has been both committed and applied to every node of the
cluster. Figure~\ref{fig:propagate1} is a scatterplot with each test
run as a red ``x" and a black line representing the average at each
cluster size.

\begin{figure}[!t]
    \begin{tikzpicture}
    \begin{axis}[%
        xlabel={Nodes}, ylabel={Time (seconds)},
        %xtick=data,
        xmin=0, ymin=0,
        grid=major,
        scatter/classes={%
            propagate_100_et1000={mark=x,draw=red},
            propagate_100_et1000_average={mark=}}]
    \addplot[scatter,only marks,%
        scatter src=explicit symbolic]%
    table[meta=label] {data/propagate_100.dat};
    \addplot[scatter,%
        scatter src=explicit symbolic]%
    table[meta=label] {data/propagate_100_average.dat};
    \end{axis}
    \end{tikzpicture}
\caption{Propagate$,$ Commit$,$ and Apply Command}
  \label{fig:propagate100}
\end{figure}

Figures \ref{fig:cluster_up}, \ref{fig:recovery-leader-failure} and
\ref{fig:recovery-half-failure} show the results of running the
\emph{test/test\_up.js} and \emph{test/test\_kill\_nodes.js} in both
modes (kill only leader and kill just under half the nodes). Three
different scatterplots are shown for each test mode to test different
values of the Raft election timeout value: 100ms, 500ms, and 1000ms.
The election timeout value makes very little difference to the average
time curve line. The reason for this is that the first leader tends to
stay the leader as new nodes are added so for the most part the
election timer does not have an impact.

@@

\begin{enumerate}
    \item \emph{Figure~\ref{fig:cluster_up}~(a)}: The results show that
        once the cluster size reaches 17, the cluster sometimes does
        not activate before the test times out (the red ``x" marks).
        Once the cluster reaches 21 nodes, all 7 test runs time out.
        The reason for this is because at 17 nodes, the leader is not
        always able to send out appendEntries RPCs to all the other
        nodes before their election timeout fires. More analysis is
        needed, but one possible explanation is that the single
        SlimerJS XULRunner process that is handling all the cluster
        nodes is not able to give enough CPU time to the leader node
        to reliably send appendEntries RPCs to all the other nodes
        within the election timeout value. Increasing the election
        timeout to 500ms or greater eliminates the failures without
        significantly changing the average cluster activation time
        curve.
    \item \emph{Figure~\ref{fig:recovery-leader-failure}~(a)}: The
        results show that when the cluster size reaches 15, then
        average amount of time for cluster recovery (after the leader
        is killed) increases dramatically (not all data points are
        shown on the plot for size 15). At cluster size 17 the cluster
        is no longer able to recover within the test timeout period.
        Increasing the election timeout to 500ms or greater eliminates
        the failures at the cost of slightly increased recovery time
        for smaller cluster sizes.
    \item \emph{Figure~\ref{fig:recovery-half-failure}~(a)}: During
        this test the cluster was unable to activate at cluster size
        21 when the election timeout value is set to 100ms (see
        Figure~\ref{fig:cluster_up}~(a)). This means there was no
        opportunity for cluster recovery at cluster size 21 so there
        is no data for that column.

@@

%\begin{figure*}[!t]
\begin{figure*}[h]
    \centering
    %\begin{subfigure}[b]{0.30\textwidth}
    \subfloat[100ms election timer]{
        \centering
        \resizebox{0.3\linewidth}{!}{
            \begin{tikzpicture}
            \begin{axis}[%
                %height=1.5\textwidth, width=1.4\textwidth,
                xlabel={Nodes}, ylabel={Time (seconds)},
                xtick=data,
                ymin=0, ymax=65,
                grid=major,
                scatter/classes={%
                    et100={mark=x,draw=blue},
                    et100_fail={mark=x,draw=red},
                    et100_average={mark=,draw=red}}]
            \addplot[scatter,only marks,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_cluster_up_100.dat};
            \addplot[scatter,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_cluster_up_100_averages.dat};
            \end{axis}
            \end{tikzpicture}
        }
        \label{fig:A}
    }
    %\begin{subfigure}[b]{0.30\textwidth}
    \subfloat[500ms election timer]{
        \centering
        \resizebox{0.3\linewidth}{!}{
            \begin{tikzpicture}
            \begin{axis}[%
                %height=1.5\textwidth, width=1.4\textwidth,
                xlabel={Nodes}, ylabel={Time (seconds)},
                xtick=data,
                ymin=0, ymax=65,
                grid=major,
                scatter/classes={%
                    et500={mark=x,draw=blue},
                    et500_average={mark=,draw=red}}]
            \addplot[scatter,only marks,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_cluster_up_500.dat};
            \addplot[scatter,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_cluster_up_500_averages.dat};
            \end{axis}
            \end{tikzpicture}
        }
        \label{fig:B}
    }
    %\begin{subfigure}[b]{0.30\textwidth}
    \subfloat[1000ms election timer]{
        \centering
        \resizebox{0.3\linewidth}{!}{
            \begin{tikzpicture}
            \begin{axis}[%
                %height=1.5\textwidth, width=1.4\textwidth,
                xlabel={Nodes}, ylabel={Time (seconds)},
                %xtick={1,3,5,7,9,11,13,15,17,19,21,23,25,27,29,31,33},
                %xticklabels={1,,5,,9,,13,,17,,21,,25,,29,,33},
                xmin=0, xmax=34,
                ymin=0, ymax=11,
                grid=major,
                scatter/classes={%
                    start_et1000={mark=x,draw=blue},
                    start_et1000_average={mark=,draw=red}}]
            \addplot[scatter,only marks,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/start_et1000.dat};
            \addplot[scatter,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/start_et1000_average.dat};
            \end{axis}
            \end{tikzpicture}
        }
        \label{fig:C}
    }
    \caption{Initial Cluster Activation}
    \label{fig:cluster_up}

@@

    %\begin{subfigure}[b]{0.30\textwidth}
    \subfloat[100ms election timer]{
        \centering
        \resizebox{0.3\linewidth}{!}{
            \begin{tikzpicture}
            \begin{axis}[%
                %height=1.5\textwidth, width=1.4\textwidth,
                xlabel={Nodes}, ylabel={Time (seconds)},
                xtick=data,
                ymin=0, ymax=3.5, xmax=23,
                grid=major,
                scatter/classes={%
                    kl={mark=x,draw=blue},
                    kl_fail={mark=x,draw=red},
                    kl_average={mark=,draw=red}}]
            \addplot[scatter,only marks,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_kill_leader_100.dat};
            \addplot[scatter,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_kill_leader_100_averages.dat};
            \end{axis}
            \end{tikzpicture}
        }
        \label{fig:D}
    }
    %\begin{subfigure}[b]{0.30\textwidth}
    \subfloat[500ms election timer]{
        \centering
        \resizebox{0.3\linewidth}{!}{
            \begin{tikzpicture}
            \begin{axis}[%
                %height=1.5\textwidth, width=1.4\textwidth,
                xlabel={Nodes}, ylabel={Time (seconds)},
                xtick=data,
                ymin=0, ymax=3.5,
                grid=major,
                scatter/classes={%
                    kl={mark=x,draw=blue},
                    kl_average={mark=,draw=red}}]
            \addplot[scatter,only marks,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_kill_leader_500.dat};
            \addplot[scatter,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_kill_leader_500_averages.dat};
            \end{axis}
            \end{tikzpicture}
        }
        \label{fig:E}
    }
    %\begin{subfigure}[b]{0.30\textwidth}
    \subfloat[1000ms election timer]{
        \centering
        \resizebox{0.3\linewidth}{!}{
            \begin{tikzpicture}
            \begin{axis}[%
                %height=1.5\textwidth, width=1.4\textwidth,
                xlabel={Nodes}, ylabel={Time (seconds)},
                %xtick=data,
                xmin=0,
                ymin=0, ymax=3.5,
                grid=major,
                scatter/classes={%
                    kill_1_et1000={mark=x,draw=blue},
                    kill_1_et1000_average={mark=,draw=red}}]
            \addplot[scatter,only marks,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/kill_1_et1000.dat};
            \addplot[scatter,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/kill_1_et1000_average.dat};
            \end{axis}
            \end{tikzpicture}
        }
        \label{fig:F}
    }
    \caption{Recovery from Leader Failure}
    \label{fig:recovery-leader-failure}

@@

    %\begin{subfigure}[b]{0.30\textwidth}
    \subfloat[100ms election timer]{
        \centering
        \resizebox{0.3\linewidth}{!}{
            \begin{tikzpicture}
            \begin{axis}[%
                %height=1.5\textwidth, width=1.4\textwidth,
                xlabel={Nodes}, ylabel={Time (seconds)},
                xtick=data,
                ymin=0, ymax=3.5, xmax=23,
                grid=major,
                scatter/classes={%
                    kh={mark=x,draw=blue},
                    kh_average={mark=,draw=red}}]
            \addplot[scatter,only marks,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_kill_half_100.dat};
            \addplot[scatter,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_kill_half_100_averages.dat};
            \end{axis}
            \end{tikzpicture}
        }
        \label{fig:G}
    }
    %\begin{subfigure}[b]{0.30\textwidth}
    \subfloat[500ms election timer]{
        \centering
        \resizebox{0.3\linewidth}{!}{
            \begin{tikzpicture}
            \begin{axis}[%
                %height=1.5\textwidth, width=1.4\textwidth,
                xlabel={Nodes}, ylabel={Time (seconds)},
                xtick=data,
                ymin=0, ymax=3.5,
                grid=major,
                scatter/classes={%
                    kh={mark=x,draw=blue},
                    kh_average={mark=,draw=red}}]
            \addplot[scatter,only marks,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_kill_half_500.dat};
            \addplot[scatter,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/data_kill_half_500_averages.dat};
            \end{axis}
            \end{tikzpicture}
        }
        \label{fig:H}
    }
    %\begin{subfigure}[b]{0.30\textwidth}
    \subfloat[1000ms election timer]{
        \centering
        \resizebox{0.3\linewidth}{!}{
            \begin{tikzpicture}
            \begin{axis}[%
                %height=1.5\textwidth, width=1.4\textwidth,
                xlabel={Nodes}, ylabel={Time (seconds)},
                xmin=0,
                ymin=0, ymax=3.5,
                grid=major,
                scatter/classes={%
                    kill_half_et1000={mark=x,draw=blue},
                    kill_half_et1000_average={mark=,draw=red}}]
            \addplot[scatter,only marks,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/kill_half_et1000.dat};
            \addplot[scatter,%
                scatter src=explicit symbolic]%
            table[meta=label] {data/kill_half_et1000_average.dat};
            \end{axis}
            \end{tikzpicture}
        }
        \label{fig:I}
    }
    \caption{Recovery from Half Cluster Failure}
    \label{fig:recovery-half-failure}
\end{figure*}
